Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-13 paper/main.tex
minor

A general problem with existing tools is user interaction. When a tool
fails to find a resource bound for a program, there is no possibility
for sound user interaction to guide the tool during bound
derivation.
For example, there is no concept of manual proofs of
resource bounds and no framework can support composition
of manually derived bounds with automatically inferred bounds.

@@

When the resource bound of a program depends on the contents of the
heap, or is non-linear (e.g. logarithmic, exponential), we propose to
introduce a \emph{logical state} using \emph{auxiliary variables}.
Auxiliary variables do not change the behavior of the program and
guide $\toolname$ during bound derivation.

>>>>

A general problem with existing tools is user interaction. When a tool
fails to find a resource bound for a program, there is no possibility
for sound user interaction to guide the tool during bound
derivation.
For example, there is no concept of manual proofs of
resource bounds; and no framework can support composition
of manually derived bounds with automatically inferred bounds.

@@

When the resource bound of a program depends on the contents of the
heap, or is non-linear (e.g. logarithmic, exponential), we propose to
introduce a \emph{logical state} using \emph{auxiliary variables}.
Auxiliary variables guide $\toolname$ during bound derivation
but they do not change the behavior of the program and
